
\section{Research plan} \label{sec:research_plan}
This section outlines the approach to be taken to continue the research and achieve the expected contributions.

Our plan includes the following stages:

\textbf{1. Literature Review}

Extend the literature review with focus on the following aspects:
\begin{itemize}
    \item XAI(Explainable AI) techniques and their application in demand forecasting.
    \item Hierarchical time-series forecasting models and their importance in demand forecasting.
    \item Application of feature importance methods in hierarchical and multi-series models.
    \item Feature importance and model reasoning in hierarchical models.
    \item Challenges and limitations of existing XAI methods.
\end{itemize}

\textbf{2. Research methodology}

\begin{itemize}
    \item Data collection: Create synthetic dataset and collect additional real-world datasets for hierarchical demand forecasting.
    \item Tool evaluation: Evaluate existing libraries for hierarchical forecasting and XAI techniques.
    \item Model implementation: Train and evaluate additional ML models for hierarchical forecasting.
    \item Feature importance analysis: Apply XAI techniques to determine feature importance and assess their impact on forecasts.
    \item Model reasoning: Analyze feature contributions to uncover underlying rules, especially at different hierarchy levels.
    \item Conduct empirical study with evaluation in terms of accuracy and computational efficiency.
\end{itemize}




