

%\subsection{Triad of model interpretability}
%The triad of model interpretability consists of model transparency, model trust, and model understanding\cite{Molnar2022}.



%\section{Local explainability}
%\label{sec:local_explainability}
%
%
%\section{Cohort explainability}
%\label{sec:cohort_explainability}
%
%
%\subsection{Global explainability}
%\label{sec:global_explainability}

\subsection{Feature importance} \label{subsec:feature-importance-in-tree-ensemble-models}
Feature importance (FI) or feature attribution is considered an interpretation method resulting in a summary statistic that assigns a score to each input feature \cite{Molnar2022}.
Depending on their scope, the FI methods can be global or local \cite{Guidotti2018,Molnar2022}.
The global feature importance (GFI) or model feature attribution methods explain the contribution of features to overall predictions, while the local FI quantifies feature contributions to specific predictions \cite{Molnar2022}.
Although related, GFI methods differ from feature selection, which identifies irrelevant features before training.
GFI methods can be model-specific, which are limited to specific model types, while model-agnostic ones are applicable independent of the model type\cite{Molnar2022}.
Another categorisation of FI methods is given by how it is calculated, in which case the importance can be based on the model's structure, while the other approach relies on a dataset.

Among the model-agnostic methods, one of the most common is permutation feature importance (PFI) which was proposed to measure FI in random forests\cite{Breiman2001}.
It is a model-agnostic, data-dependent method that measures the decrease in the model's performance when the features are permuted.
The PFI can be calculated using different metrics such as the mean squared error (MSE), the mean absolute error (MAE), or the coefficient of determination ($R^2$).
PFI also has limitations, as it is sensitive to over- and underfitting\cite{molnar2020limitations}, in which case the FI differs on training and test data, so the use of both datasets can be beneficial.
In addition, another flaw of the PFI method is that it can generate cases in which the model does not have training data\cite{Molnar_2020_pitfalls,giles_hooker_unrestricted_2021},
but other methods were proposed to overcome this\cite{ian_covert_understanding_2020, kristin_blesch_conditional_2023}.
% todo include conditional PFI

SHAP(SHapley Additive exPlanation)\cite{scott_lundberg_unified_2017} values contribute local explanation for individual predictions, but aggregates of it are useful to assess the importance of global features.
For example, the mean absolute SHAP values quantify the importance of the feature regardless of the direction of the impact on the prediction.
There are different algorithms for approximation from which Kernel SHAP\cite{scott_lundberg_unified_2017} is one that is model-agnostic.
TShap \cite{vikas_c_raykar_tsshap_2023} is a method for estimating SHAP values for time series data, but it uses a surrogate model, so it gives the FI of the surrogate.
Another related method is SAGE \emph{(Shapley additive global importance)} \cite{ian_covert_understanding_2020}, which estimates the contribution of each feature to the model's performance.

Tree specific GFI methods are gain-based importance values which were already introduced with decision trees \cite{gordon_classification_1984}
It measures of the reduction in mean average error(MAE) made by the decisions based on the respective feature.
Another measure is the split-based importance\cite{tianqi_chen_xgboost_2016} refers to the number of decisions made by the model based on a feature.
The previously presented SHAP also has a tree model-specific solution for approximation, called TreeSHAP \cite{scott_lundberg_local_2020}

\subsection{Global feature importance}

We denote any machine learning model $f$ that predicts the target variable $y$ based on the input features $x = [x^1, x^2, ..., x^n]$.
GFI of $f$ is a measure of importance attributed to each $X=[X^1, X^2, ..., X^n]$ feature in overall.
noted as $ \phi( f, X) = [ \phi( f, X^1), \phi( f, X^2), ..., \phi( f, X^n)]$.
The model $f$ is trained on the training set $D_{\text{train}}$ and evaluated on the test set $D_{\text{test}}$.

For example, PFI measures the importance of a feature by shuffling the values of the feature and observing the change in the model's performance:
$\phi(f, X_i)_{PFI} = L(f, D_{\text{test}}) - L(f, D_{\text{test}}^{X_i})$,
where $D_{\text{test}}^{X_i}$ is the test set with the values of the feature $X_i$ shuffled, and $L$ is the loss function used to train the model.
If MSE is used as the loss function, PFI is $\phi(f, X_i) = MSE(f, D_{\text{test}}) - MSE(f, D_{\text{test}}^{X_i})$.

To make the importance values comparable, we introduce the concept of relative importance, which is the ratio of the importance of a feature to the sum of all feature importances.
The relative importance of a feature $X_i$ is calculated as:
$$
\text{RI}(f, X_i) = \frac{\phi(f, X_i)}{\sum_{j=1}^{n} \phi(f, X_j)}
$$
Also the rank of the feature importance can be calculated as the order of the feature importance values.




\subsection{Feature importance as a basis for model reasoning}\label{subsec:feature-importance-as-basis-for-model-reasoning}
Feature importance methods can provide insight into the model's decision-making process and help to understand the underlying rules and reasoning behind the predictions.
By including demand drivers as features in the model, the feature importance methods can help to identify the key drivers of demand.
For external factors such as weather, holidays, and economic indicators, the importance of the characteristics can help to understand their impact on demand.
Through internal factors like price, promotions, the feature importance can help to understand post-promotion effects and the impact of price changes on the demand\cite{vandeput2023demand}.
Knowing the influence of internal factors can help to optimize pricing strategies and promotional activities.
However, causation and correlation are different concepts, and the feature importance methods can only provide correlation;
therefore, the identified key features should be further analyzed to understand the causation\cite{Breiman2001}





